\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY

### 2016-05-09 draft.tex
add probabilistic voting reference to Roemer (1997)

This work relates to the literature on vote-buying and legislative behavior in political science (Groseclose and Snyder (1996), Dekel et. al. (2005), Dal Bo (2007)) as well as to the canonical studies on endogenous regulation (cf. Stigler (1975), Peltzman (1976), Becker (1983), Laffont and Tirole (1994)).

@@

>>>>

This work relates to the literature on vote-buying and legislative behavior in political science (Groseclose and Snyder (1996), Dekel et. al. (2005), Dal Bo (2007)) as well as to the canonical studies on endogenous regulation (cf. Stigler (1975), Peltzman (1976), Becker (1983), Laffont and Tirole (1994)).  By putting legislators in the place of voters and lobbyists in the place of candidates, the idea can been seen as similar to that of the probabilistic voting models that incorporate policy motivation such as Roemer (1997).

@@

\item Roemer, J. (1997), ``Political-economic Equilibrium when Parties Represent Constituents: The Unidimensional Case.'' {\em Social Choice and Welfare} 14, 479-502.
